### 2020-01-25 ChapterImplementation/chapterImplementation.tex
Updated: Start of future architectures

\begin{figure}[h]
	\centering
	\resizebox{\linewidth}{!}{\input{Figs/Architecture.pdf_tex}}
	%\scalebox{1.1}{\input{Figs/Architecture.pdf_tex}}
	\caption{Server Breakdown. This diagram shows a breakdown of the components of an individual server.}
	\label{fig_stack}
\end{figure}

\subsection{Future Architecture}

\begin{figure}
	\centering
	\scalebox{1.25}{\input{Figs/OverseerNode.pdf_tex}}
	\caption{Overseer node.}
\end{figure}

\begin{figure}
	\centering
	\scalebox{1.25}{\input{Figs/MultipleOverseerNodes.pdf_tex}}
	\caption{Multiple overseer nodes for scalable number of players.}
\end{figure}

>>>>

\begin{figure}[t]
	\centering
	\resizebox{\linewidth}{!}{\input{Figs/Architecture.pdf_tex}}
	%\scalebox{1.1}{\input{Figs/Architecture.pdf_tex}}
	\caption{Server Breakdown. This diagram shows a breakdown of the components of an individual server.}
	\label{fig_stack}
\end{figure}

\subsection{Future Architecture}
System architectures which could be investigated in the future will now be proposed and discussed. A limitation of the current architecture is that a client must connect to all servers; servers that are responsible for running the simulation also have the overhead of connecting to many clients. An alternative to this is to make the use of an `overseer' node, which acts as a middle-man for communication with all the servers, as illustrated in Fig. \ref{OverseerNode}. The overseer node is co-located in the cloud with the simulation servers. The clients all connect to the overseer node, but all the servers only connect to one overseer node, reducing the overhead of many clients connecting to a server, freeing up computational resources on each simulation server, allowing more resources to be used for the simulation itself. An additional advantage of this approach is it allows for some fault-tolerance. If one or more simulation servers were to fail, the overseer node has a copy of the states of all objects from those servers, meaning those spatial partitions of the simulation could be restored. The disadvantage of using an overseer node is the additional latency between client and simulation server, messages now have to be processed by the overseer node between the simulation servers and clients. For example, if a replicated object moves in one of the simulation servers, the update message for that object has to be processed and sent by the simulation server, sent over the network to the overseer, received and processed by the overseer node and then sent over the network to all connected clients. The additional latency is due to the communication latency between simulation server and overseer node and the time taken to process messages on the overseer node.

\begin{figure}
	\centering
	\scalebox{1.25}{\input{Figs/OverseerNode.pdf_tex}}
	\caption{Overseer node.}
	\label{OverseerNode}
\end{figure}

The limitation of the use of an overseer node is the number of clients that can connect is limited to the amount that can be handled by a single overseer node. In order to enable a scalable number of clients, multiple overseer nodes could be employed, dividing the workload between overseer nodes, allowing for many more clients to connect. This is illustrated in \ref{MultiOverseer}.

\begin{figure}
	\centering
	\scalebox{1.25}{\input{Figs/MultipleOverseerNodes.pdf_tex}}
	\caption{Multiple overseer nodes for scalable number of clients.}
	\label{MultiOverseer}
\end{figure}
